A generalization of the Bradley-Terry model for draws in chess with an application to collusion

### 2021-01-18 inst/skating_analysis.Rmd
consistentification of skating dataset

```{r,dpi=72}
par(pty='s')
lik <- rank(-m)
plot(1:23,lik,asp=1,pch=16,xlab='official order',ylab='likelihood order')
text(1:23,lik,asp=1,pch=16,pos=c(rep(4,19),rep(2,4)),rownames(skating_table))
abline(0,1)
```

>>>>

```{r,dpi=72}
 rL <- sort(skating_maxp,decreasing=TRUE)
 rL[] <- seq_along(rL)
 rO <- seq_len(nrow(skating_table))
 names(rO) <- rownames(skating_table)
 ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="Ladies free skating, 2002 Winter Olympics")
```
